---
title: "p8105_hw2_yy3020"
author: "YuaoYang"
date: "2019/9/25"
output: github_document
---

```{r }
library(readxl)
library(tidyverse)
```

```{r}
#clear the trash_data
trash_data = read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "Mr. Trash Wheel", col_names = TRUE) %>%
janitor::clean_names() %>%
  select(1:14) %>%
  drop_na() %>%
  mutate(sports_balls = round(sports_balls, 0),
         sports_balls = as.integer(sports_balls)) 

```


```{r}
pp_2017 = read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2017 Precipitation", skip = 1) %>%
   janitor::clean_names() %>% 
  drop_na() %>%
  mutate('year'=2017) %>% 
  mutate(month = month.name[month]) %>%
  select(year, everything())

pp_2018 = read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2018 Precipitation", skip = 1) %>%
   janitor::clean_names() %>% 
  drop_na()  %>%
  mutate('year'=2018) %>% 
  mutate(month = month.name[month]) %>% 
  select(year,everything())

new_pp = rbind(pp_2017, pp_2018) 

```

the number of observations in trash_data is (`r nrow(trash_data) `) and in new_pp is (`r nrow(new_pp)`). The key variables are(`r colnames(trash_data[5:14])`) in trash_data, and the key variables are (`r colnames(new_pp)`).The total precipitation in 2018 is (`r sum(pull(pp_2018,total)) `)。the median number of sports balls in a dumpster in 2017 is (`r filter(trash_data, year == 2017) %>% pull(sports_balls) %>% median `). 


#Problem 2
```{r}
pols_month = read_csv("./data/pols-month.csv") %>%
  janitor::clean_names() %>%
   separate(mon, into = c("year", "month","day")) %>%
  mutate(year = as.integer(year),
         month = as.integer(month),
         day = as.integer(day)) %>%
  pivot_longer(c(prez_gop, prez_dem),
               names_to = "president",
               names_prefix = "prez_"
               ) %>%
select(-day)
 

  
```

```{r}
snp = read_csv("./data/snp.csv") %>%
  janitor::clean_names() %>%
   separate(date, into = c("month", "day","year")) %>%
  mutate(year = as.integer(year),
         month = as.integer(month)) %>%
           arrange(year,month) %>%
  select(year, month, close)
 
```

````{r}
unemplo = read_csv("./data/unemployment.csv") %>%
  janitor::clean_names() %>%
 transmute("year" = year,
          "1" = jan, 
           "2" = feb,
           "3" = mar,
           "4" = apr,
           "5" = may,
           "6" = jun,
           "7" = jul,
           "8" = aug,
           "9" = sep,
           "10" = oct,
           "11" = nov,
           "12" = dec) %>%
  pivot_longer(2:13,
               names_to = "month",
               values_to = "unemplyment") %>%
   mutate(year = as.integer(year),
         month = as.integer(month))

snp_pols = full_join(snp, pols_month, by = c("year", "month"))
snp_pols_unem = full_join(snp_pols, unemplo, by = c("year", "month"))

```
```{r}
range_year = range(pull(snp_pols_unem,year))
```

From these datasets pols_month,  we can find that there are there are so many variables like  (`r colnames(pols_month) `). From snp, we can find there are (`r colnames(snp) `). From umemplo, we can find there are (`r colnames(unemplo) `). The dimension of resulting dateset snp_pols_unem is (`r nrow(snp_pols_unem) `, `r ncol(snp_pols_unem)`). The range is (`r range_year[2] - range_year[1]` ). The names of  key variables are (`r colnames(snp_pols_unem[3:12])`).

#problem 3
```{r}
baby_name = read_csv("./data/Popular_Baby_Names.csv") %>%
  janitor::clean_names() %>%
  mutate(childs_first_name = str_to_title(childs_first_name),
         gender = str_to_lower(gender),
         ethnicity = recode(str_to_lower(ethnicity),
                            "asian and paci" = "asian and pacific islander",
                            "black non hisp" = "black non hispanic",
                            "white non hisp" = "white non hispanic" ) ) %>%
  distinct() %>%
  rename(
    birth_year = year_of_birth,
    race = ethnicity,
    first_name = childs_first_name
  )
         
  
```

```{r}
olivia <- filter(baby_name, first_name == "Olivia", gender == "female") %>%
  pivot_wider(id_cols = "race",
              names_from = "birth_year",
              values_from = "rank")
ovila2 <- filter(baby_name, first_name == "Olivia", gender == "female") %>%
  pivot_wider(id_cols = "birth_year",
              names_from = "race",
              values_from = "rank")

most_popular_male_names <- filter(baby_name, gender == "male") %>% 
  group_by(birth_year,race) %>% 
  slice(which.min(rank)) %>%
  select(c(1,3,4))%>%
  pivot_wider(
            id_cols = "race",
            names_from = "birth_year",
            values_from = "first_name")


```

```{r}
wnh_male = filter(baby_name, gender == "male", race == "white non hispanic", birth_year == "2016")
ggplot(wnh_male, aes(x = rank, y = count)) +geom_point()
```
